### 2016-04-19 text/ms.Rmd
And back ROC section in the results
Fix 2 figure labels
Insert basic performance measures in the results

Ensemble methods, and in particular the machine learning superensemble models
(random forest and GBM), generally improved estimates of status and trend over
any individual model (Fig. \ref{hexagon}e--h, Fig. \ref{scatter-sim-slope}e--h).
Compared to the individual models, machine learning superensembles improved
accuracy (median absolute proportional error) by
`r mean_sim$mach_vs_ind_mare_fold`%, increased rank-order correlation from
`r mean_sim$ind_corr_range` to `r mean_sim$mach_corr_range`, and reduced bias
(median proportional error) from `r mean_sim$ind_mre_range` to
`r mean_sim$mach_mre_range` (Fig. \ref{performance}a).
Results were similar when predicting trend: compared to individual models,
machine learning superensembles improved accuracy by
`r slope_sim$mach_vs_ind_mare_fold`%, increased rank-order correlation from
`r slope_sim$ind_corr_range` to `r slope_sim$mach_corr_range`, and reduced
bias from `r slope_sim$ind_mre_range` to `r slope_sim$mach_mre_range` (Fig.
\ref{performance-sim-slope}).
The ensemble models that simply took a mean of the individual models ranked
slightly behind the best individual model for estimating fish stock status
(CMSY; Fig. \ref{performance}a) and had slightly lower correlation but higher
accuracy than the best individual model at predicting the trends of status
(SSCOM; Fig. \ref{performance-sim-slope}).

The superensemble models were able to improve the predictive performance by
harnessing the best properties of individual models, the covariance between
individual models, and interactions with other covariates. For example, SSCOM
had strong predictive ability when it predicted low $B/B_\mathrm{MSY}$ (Fig.
\ref{hexagon}c, Fig. \ref{partial-sim}c) and CMSY predictions were
approximately linearly related to $B/B_\mathrm{MSY}$ within the low and high
clusters of predictions (Fig. \ref{partial-sim}). Superensembles also exploited
the covariance between individual model predictions. For instance, both the
linear model and GBM ensemble suggest that if mPRM and SSCOM predict high
status, the true status also tends to be high (Figs \ref{lm-coefs},
\ref{partial-2d-sim}l). The addition of spectral density covariates helped the
superensemble models correctly predict higher status values (Fig.
\ref{hexagon-sim-covariance}g, h). The performance of the ensembles was only
marginally improved by including these covariates (Fig.
\ref{performance-with-covariance} vs. Fig. \ref{performance}.

>>>>

Ensemble methods, and in particular the machine learning superensemble models
(random forest and GBM), generally improved estimates of status and trend over
any individual model (Fig. \ref{hexagon}e--h, Fig. \ref{scatter-sim-slope}e--h).
Compared to the individual models, machine learning superensembles improved
accuracy (median absolute proportional error) by
`r mean_sim_basic$mach_vs_ind_mare_fold`%, increased rank-order correlation from
`r mean_sim_basic$ind_corr_range` to `r mean_sim_basic$mach_corr_range`, and reduced bias
(median proportional error) from `r mean_sim_basic$ind_mre_range` to
`r mean_sim_basic$mach_mre_range` (Fig. \ref{performance}a).
These superensembles also generally had better ability to distinguish if
simulated stocks were above or below $B/B_\mathrm{MSY} = 0.5$ (Fig. \ref{roc-sim}).
Results were similar when predicting trend: compared to individual models,
machine learning superensembles improved accuracy by
`r slope_sim$mach_vs_ind_mare_fold`%, increased rank-order correlation from
`r slope_sim$ind_corr_range` to `r slope_sim$mach_corr_range`, and reduced
bias from `r slope_sim$ind_mre_range` to `r slope_sim$mach_mre_range` (Fig.
\ref{performance-sim-slope}).
The ensemble models that simply took a mean of the individual models ranked
slightly behind the best individual model for estimating fish stock status
(CMSY; Fig. \ref{performance}a) and had slightly lower correlation but higher
accuracy than the best individual model at predicting the trends of status
(SSCOM; Fig. \ref{performance-sim-slope}).

The superensemble models were able to improve the predictive performance by
harnessing the best properties of individual models, the covariance between
individual models, and interactions with other covariates. For example, SSCOM
had strong predictive ability when it predicted low $B/B_\mathrm{MSY}$ (Fig.
\ref{hexagon}c, Fig. \ref{partial-sim}c) and CMSY predictions were
approximately linearly related to $B/B_\mathrm{MSY}$ within the low and high
clusters of predictions (Fig. \ref{partial-sim}). Superensembles also exploited
the covariance between individual model predictions. For instance, both the
linear model and GBM ensemble suggest that if mPRM and SSCOM predict high
status, the true status also tends to be high (Figs \ref{lm-coefs},
\ref{partial-2d-sim}l). The addition of spectral density covariates helped the
superensemble models correctly predict higher status values (Fig.
\ref{hexagon-sim-covariates}g, h). The performance of the ensembles was only
marginally improved by including these covariates (Fig.
\ref{performance-with-covariates} vs. Fig. \ref{performance}).
